Distinguishing Spin-Aligned and Isotropic Black Hole Populations With Gravitational Waves

### 2017-06-03 paper/AlignedIsotropicGW.tex
Minor text fix in section 8.

\section{Precision of $\chieff$ measurements}
\label{sec:chi-eff-precision}
Throughout this work we have made the simplifying assumption that the
precision to which $\chieff$ can be constrained for individual binaries
is independent of the binary's properties.  In practice, our ability to
constrain $\chieff$ \emph{is} dependent on the system's properties, in
particular its true $\chieff$ and mass ratio, which we illustrate in
figure \ref{fig:chi-eff-constraints}.

@@

By neglecting these effects we do not expect to qualitatively affect
out conclusions, though they could affect predictions for the total
number of detections necessary to constrain the population.  For
example, if the universe preferentially forms asymmetric binaries with
low mass ratios, individual $\chieff$ constraints will be systematically
worse, requiring more binaries to infer the properties
of the population.

>>>>

\section{Precision of $\chieff$ measurements}
\label{sec:chi-eff-precision}
Throughout this work we have made the simplifying assumption that the
precision to which $\chieff$ can be constrained for individual binaries
is independent of the binary's properties.  In practice, our ability to
constrain $\chieff$ \emph{is} dependent on the system's properties, in
particular its true $\chieff$ and mass ratio, which we illustrate in
Extended Data Figure \ref{fig:chi-eff-constraints}.

@@

We do not expect these effects to qualitatively affect
out conclusions, though they could affect predictions for the total
number of detections necessary to constrain the population.  For
example, if the universe preferentially forms asymmetric binaries with
low mass ratios, individual $\chieff$ constraints will be systematically
worse, requiring more binaries to infer the properties
of the population.
